Implementation of Concurrent Hash Tables in Java

### 2022-03-25 paper.tex
Finished Appendix

\begin{abstract}
Abstract goes here.
\end{abstract}

@@

\section{Related work}
I've seen a similar problem before

\section{Contributions}
I've fixed this problem once

@@

\section{Experimental Results}
Well, it worked on my machine.

\section{Appendix}

>>>>

\begin{abstract}

\end{abstract}

@@

@@

\section{Experimental Results}
We begin by testing how the standard hash table will performed when run sequentially, and then when multithreaded.

\section{Appendix}
\subsection{Challenges}
One of the major challenges the group came across was learning how to do concurrent programming within Java, as most of the group member's experience
lay in C++.
\subsection{Completed Tasks}
\begin{itemize}
    \item Creating a standard hash table.
    \item Creating a hash table with locks.
\end{itemize}
\subsection{Remaining Tasks}
\begin{itemize}
    \item Creating a lockfree hash table.
    \item More experimental testing.
\end{itemize}
